Collective excitations in competing phases in two and three dimensions

### 2023-12-07 paper/main.tex
xy

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%                                                  Abstract                                                 %%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
    We investigate the superconducting (SC), charge-density wave (CDW), and antiferromagnetic (AFM) phases 
    in the extended Hubbard model at zero temperature and half-filling.
    We employ the iterated equations of motion approach \cite{Kalthoff17,bleicker18} to compute the two-particle Green's functions and
    by extension, the corresponding spectral densities.
    This renders a comprehensive analysis of the behaviour of collective excitations possible
    as the model's parameters are changed across phase transitions.
    We identify the well-known amplitude (Higgs) and phase (Leggett) modes within the 
    superconducting phase and observe a similar excitation in the CDW phase
    which shift towards zero energy as the system approaches the phase transition to the SC phase.
    In the CDW phase, close to the phase transition to the AFM phase, we find a collective mode 
    which does not change significantly and another modes which becomes soft
    as the phase boundary is approached.
\end{abstract}

@@

The remainder of this paper is organized as follows:
In \autoref{sec:model} we will introduce the model and its Hamiltonian as well our mean-field theory.
A brief overview over the iterated equations of motion approach is presented in \autoref{sec:ieom}.
Next, we show our results in \autoref{sec:results}.
Lastly, in \autoref{sec:conclusion}, we will discuss our results.
In the appendix \textcolor{red}{(or in the supplemental material?)}, we will derive and explain our methods in detail.

@@

The Hamiltonian of the extended Hubbard model is given by
\begin{equation}
    \label{eqn:full_hamiltonian}
    \begin{aligned}
        H = &-t \sum_{\langle i, j \rangle, \sigma} \left( c_{i\sigma}^\dagger c_{j\sigma} + \text{h.c.} \right) 
        + \mu \sum_{i,\sigma} n_{i\sigma} \\
        &+ U \sum_{i} n_{i\uparrow} n_{i\downarrow} 
        + \frac{V}{2} \sum_{\langle i, j\rangle, \sigma} n_{i\sigma} n_{j\sigma}\,,
    \end{aligned}
\end{equation}
where $c_{i\sigma}^{(\dagger)}$ annihilates (creates) an electron with spin $\sigma$ on lattice site $i$ 
and $\langle i, j\rangle$ denotes the summation over next neighbours.
The parameters are the hopping amplitude $t$, the onsite interaction $U$, the intersite interaction $V$ and the chemical potential $\mu$.
Applying a Fourier transformation into $k$-space yields the single-particle dispersion 
\begin{equation}
    \epsilon_0 (\vk) = -2t \sum_{\alpha=1}^D \cos(k_\alpha)\,,\quad k_\alpha \in [-\pi, \pi)\,,
\end{equation}
with the system's dimension $D$ and the dimensionless momentum $\vk$.

@@

Next, we decouple the the interaction terms.
We define 
\begin{equation}
    \label{eqn:operators}
    \begin{aligned}
        n_{k\sigma} &\coloneqq  c_{\vk\sigma}^\dagger c_{\vk\sigma}\,,      &f_k     &\coloneqq  c_{-\vk\down} c_{\vk\up}\,, \\
        g_{k\sigma} &\coloneqq  c_{\vk\sigma}^\dagger c_{\vk+\vQ\sigma}\,,  &\eta_k  &\coloneqq  c_{-\vk-\vQ\down} c_{\vk\up}\,,
    \end{aligned}
\end{equation}
where $\vQ \coloneqq  (\pi, ...)$ defines the nesting vector for the CDW and AFM phases, see Ref. \cite{sentef17}.
We use the following abbreviations to write down the mean-field parameters
\begin{subequations}
    \begin{align}
        \label{eqn:delta_cdw}
        \Delta_\text{CDW} &= \left(\frac{U}{2N} - \frac{zV}{N}\right) \sum_{\vk\sigma} \langle g_{\vk\sigma} \rangle\,, \\
        \label{eqn:delta_afm}
        \Delta_\text{AFM} &= \frac{U}{2N} \sum_{\vk} \left( \langle g_{k\uparrow} \rangle - \langle g_{\vk\downarrow} \rangle \right)\,, \\
        \Delta_\text{SC} &= \frac{U}{N} \sum_{\vk} \langle f_{\vk} \rangle\,, \\
        \Delta_\eta &= \frac{U}{N} \sum_{\vk} \langle \eta_{\vk} \rangle\,, \\
        \Delta_n &= \frac{V}{N} \sum_{\vk,\sigma} \sum_{\alpha=1}^D \cos k_\alpha \langle n_{\vk\sigma} \rangle\,,
    \end{align}
\end{subequations}
where $z$ denotes the coordination number of the lattice.
The last parameter, $\Delta_n$, renormalizes the hopping term to
\begin{equation}
    \epsilon( \vk ) \coloneqq  -(2 + \Delta_n) \sum_{\alpha=1}^D \cos(k_\alpha)\,.
\end{equation}
In total, we obtain the mean-field Hamiltonian in spinor representation as
\begin{equation}
    \label{eqn:mf_hamiltonian}
    H_\text{MF} = \sum_{\vk} \Psi^\dagger (\vk) h(\vk) \Psi (\vk)\,,
\end{equation}
with the spinors
\begin{equation}
    \Psi^\dagger (\vk) \coloneqq  \left( c_{\vk\up}^\dagger\,, c_{\kplusQ\up}^\dagger\,, c_{-\vk\down}\,, c_{\kminusQ\down} \right)
\end{equation}
and 
\begin{equation}
    h(\vk) \coloneqq  \begin{pmatrix}
        \epsilon (\vk) & \Delta_-^* & \Delta_\text{SC} & \Delta_\eta \\
        \Delta_- & \epsilon (\vk + \vQ) & \Delta_\eta & \Delta_\text{SC} \\
        \Delta_\text{SC}^* & \Delta_\eta^* & - \epsilon (-\vk) & - \Delta_+ \\
        \Delta_\eta^* & \Delta_\text{SC}^* & - \Delta_+^* & - \epsilon (-\vk - \vQ)
        \end{pmatrix}\,,
\end{equation}
where we defined $\Delta_\pm \coloneqq  \Delta_\text{CDW} \pm \Delta_\text{AFM}$.

@@

We solve the mean-field equations self-consistently.
The $\gamma$-integrals are approximated numerically using a $\tanh$-$\sinh$ quadrature \cite{takahasi73}, 
terminating once $|1 - \int \dgamma \rho(\gamma)| < 10^{-13}$ and reusing the computed points and weights.
This method excells at dealing with the singularities in the DOS, 
requiring merely a few hundred function evaluations to achieve the desired accuracy.

This procedure yields the groundstate phase diagram at temperature $T=0$ shown in \autoref{fig:phase_diagram}.
The CDW-AFM boundary is located at $U = zV$, where $z$ is the coordination.
This holds for both the square lattice ($z=4$) and the simple cubic lattice ($z=6$) and can be seen by comparing \eqref{eqn:delta_cdw} and \eqref{eqn:delta_afm}:
Crossing the aforementioned line, changes which one of the two prefactors is larger.

@@

So far we have discussed the static mean-field equations that essentially describe the static groundstate.
These results will be used to compute the quantities, namely expectation values, necessary for the iterated equations of motion approach \cite{uhrig09,hamerla13,hamerla14,bleicker18}.
With it, we can describe two-particle quantities like the various collective excitations of the system.
We will present the general ideas briefly here and refer the interested reader to the appendix \textcolor{red}{!REF!} for a detailed explanation and derivation.

@@

However, most Hamiltonians do not allow any such operator set to exist as the commutation usually introduces terms of higher order.
For instance, a commuting a bilinear term with a quartic Hamiltonian yields, quartic terms. Repeating the commutation yields hexartic ones and so on.
Therefore, one repeats this commutation process and includes the occurring terms within a bigger set,
hoping to get better results as the set size increases.

@@

To study the collective excitation, we investigate various retarded Green's functions 
\begin{equation}
    G_{AB}^\text{ret} (t) = - i \langle [A(t), B] \rangle \Theta(t)\,,
\end{equation}
where $\Theta(t)$ is the Heaviside function, and their Fourier transformed
\begin{equation}
    \label{eqn:standard_gf}
    G_{AB}(\omega + i0^+) = -i \int_0^{\infty} e^{izt} \langle [A(t), B] \rangle \mathrm{d}t\,.
\end{equation}
Our previous choice of pseudo scalar product enables us to write down a matrix-valued Green's functions in terms of the aforementioned matrices
\begin{align}
    \label{eqn:green_function}
    \mathcal{G}(z &= \omega + i0^+) = \mN \frac{1}{-z \mN - \mM} \mN \\
        &\coloneqq  -\mN \mathcal{R}(z) \mN\,,
\end{align}
where we used the resolvent
\begin{equation}
    \label{eqn:resolvent}
    \mathcal{R}(z) \coloneqq  \frac{1}{z \mN + \mM}\,.
\end{equation}
The entries of this matrix $\mathcal{G}(z)$ are the Fourier transformed Green's functions mentioned in \eqref{eqn:standard_gf} with respect to the operators from the initially chosen set.
For instance, assume the operator in the set is $f_{\vk}$, then the top left element of $\mathcal{G}$ is the Green's function 
\begin{equation}
    \mathcal{G}_{00}(z = \omega +i0^+) =  G(z) = -i \int_0^{\infty} \langle [f_{\vk}(t), f_{\vk}^\dagger(0)] \rangle e^{izt} \mathrm{d}t\,.
\end{equation}
For a detailed derivation of this statement, we refer the reader to the appendix \textcolor{red}{!REF!}.

Our operator set consists of operators of the type
\begin{equation}
    A_\gamma \coloneqq  \frac{1}{\sqrt{N}} \sum_{\vk} \delta (\gamma - \hat{\gamma}( \vk )) A_{\vk}\,,
\end{equation}
where $A_{\vk}$ represents each type of operator in \eqref{eqn:operators} and their Hermitian conjugates.
Different indices are taken as additional set operators, e.g. $n_{\vk \up}$ and $n_{\vk \down}$ are taken into the set separately.
We then order these operators in a way reminiscent of the $x$- and $p$-terms in the harmonic oscillator, i.e.
\begin{equation}
    X_i \coloneqq  A_i + A_i^\dagger\,,\quad P_i \coloneqq  A_i - A_i^\dagger\,.
\end{equation}
Our set is then $\mathcal{B}_{XP} \coloneqq  {X_i, P_i}$.
If some operators would be 0 ($P_i$ for any $n$-type term) or duplicates (certain $X_i$ for $g$-type terms), we omit them.

@@

There are a variety of different features. The difference between the two lattices is mostly quantitative in nature.
First and foremost, in the SC phase, there is a sharp peak located at $\omega=0$, only in the phase spectral function,
and another peak, only in the amplitude spectral function, located at $\omega=2\Delta_\text{SC}$.
We identify them with the well-known Leggett and Higgs modes in superconductors.
In the CDW phase, both of these spectral functions become identical and form a sharp peak below the two-particle continuum.

@@

\begin{figure*}
    \centering
    \includegraphics[width=.98\textwidth]{plots/sc_peak_in_cdw_position.pdf}
    \caption{The upper panels show double logarithmic plots of the positions $\omega_0$ of the SC peak in the CDW phases while the lower panels show their respective weights $w_0 = e^{b}$.
    The left column shows the results for the square and the right column for the simple cubic lattice at $U=-2.5$.
    The fits are linear, i.e., $y(V) = c \ln(V/t) + d$ and the parameters are printed on the individual panals.}
    \label{fig:sc_in_cdw_behaviour}
\end{figure*}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%                                                  Abstract                                                 %%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
    We investigate the superconducting (SC), charge-density wave (CDW), and antiferromagnetic (AFM) phases 
    in the extended Hubbard model at zero temperature and half-filling.
    We employ the iterated equations of motion approach \cite{Kalthoff17,bleicker18} to compute the two-particle Green's functions and by extension, the corresponding spectral densities.
    This renders comprehensive analysis of the behaviour of collective excitations possible as the model's parameters are changed across phase transitions.
    We identify the well-known amplitude (Higgs) and phase (Leggett) modes within the superconducting phase and observe a similar excitation in the CDW phase which shifts towards zero energy as the system approaches the phase transition to the SC phase.
    In the CDW phase, close to the phase transition to the AFM phase, we find a collective mode that does not change significantly and another mode that becomes soft as the phase boundary is approached.
\end{abstract}

@@

The remainder of this paper is organized as follows:
In \autoref{sec:model} we will introduce the model and its Hamiltonian as well as our mean-field theory.
A brief overview of the iterated equations of motion approach is presented in \autoref{sec:ieom}.
Next, we show our results in \autoref{sec:results}.
Lastly, in \autoref{sec:conclusion}, we will discuss our results.
In the appendix \textcolor{red}{(or in the supplemental material?)}, we will derive and explain our methods in detail.

@@

The Hamiltonian of the extended Hubbard model is given by
\begin{equation}
    \label{eqn:full_hamiltonian}
    \begin{aligned}
        H = &-t \sum_{\langle i, j \rangle, \sigma} \left( c_{i\sigma}^\dagger c_{j\sigma} + \text{h.c.} \right) 
        + \mu \sum_{i,\sigma} n_{i\sigma} \\
        &+ U \sum_{i} n_{i\uparrow} n_{i\downarrow} 
        + \frac{V}{2} \sum_{\langle i, j\rangle, \sigma} n_{i\sigma} n_{j\sigma}\,,
    \end{aligned}
\end{equation}
where $c_{i\sigma}^{(\dagger)}$ annihilates (creates) an electron with spin $\sigma$ on lattice site $i$ 
and $\langle i, j\rangle$ denotes the summation over next neighbours.
The parameters are the hopping amplitude $t$, the onsite interaction $U$, the intersite interaction $V$, and the chemical potential $\mu$.
Applying a Fourier-transformation into $k$-space yields the single-particle dispersion 
\begin{equation}
    \epsilon_0 (\vk) = -2t \sum_{\alpha=1}^D \cos(k_\alpha)\,,\quad k_\alpha \in [-\pi, \pi)\,,
\end{equation}
with the system's dimension $D$ and the dimensionless momentum $\vk$.

@@

Next, we decouple the interaction terms.
We define 
\begin{equation}
    \label{eqn:operators}
    \begin{aligned}
        n_{k\sigma} &\coloneqq  c_{\vk\sigma}^\dagger c_{\vk\sigma}\,,      &f_k     &\coloneqq  c_{-\vk\down} c_{\vk\up}\,, \\
        g_{k\sigma} &\coloneqq  c_{\vk\sigma}^\dagger c_{\vk+\vQ\sigma}\,,  &\eta_k  &\coloneqq  c_{-\vk-\vQ\down} c_{\vk\up}\,,
    \end{aligned}
\end{equation}
where $\vQ \coloneqq  (\pi, ...)$ defines the nesting vector for the CDW and AFM phases, see Ref. \cite{sentef17}.
We use the following abbreviations to write down the mean-field parameters
\begin{subequations}
    \begin{align}
        \label{eqn:delta_cdw}
        \Delta_\text{CDW} &= \left(\frac{U}{2N} - \frac{zV}{N}\right) \sum_{\vk\sigma} \langle g_{\vk\sigma} \rangle\,, \\
        \label{eqn:delta_afm}
        \Delta_\text{AFM} &= \frac{U}{2N} \sum_{\vk} \left( \langle g_{k\uparrow} \rangle - \langle g_{\vk\downarrow} \rangle \right)\,, \\
        \Delta_\text{SC} &= \frac{U}{N} \sum_{\vk} \langle f_{\vk} \rangle\,, \\
        \Delta_\eta &= \frac{U}{N} \sum_{\vk} \langle \eta_{\vk} \rangle\,, \\
        \Delta_n &= \frac{V}{N} \sum_{\vk,\sigma} \sum_{\alpha=1}^D \cos k_\alpha \langle n_{\vk\sigma} \rangle\,,
    \end{align}
\end{subequations}
where $z$ denotes the coordination number of the lattice.
The last parameter, $\Delta_n$, renormalizes the hopping term to
\begin{equation}
    \epsilon( \vk ) \coloneqq  -(2 + \Delta_n) \sum_{\alpha=1}^D \cos(k_\alpha)\,.
\end{equation}
In total, we obtain the mean-field Hamiltonian in spinor representation as
\begin{equation}
    \label{eqn:mf_hamiltonian}
    H_\text{MF} = \sum_{\vk} \Psi^\dagger (\vk) h(\vk) \Psi (\vk)\,,
\end{equation}
with the spinors
\begin{equation}
    \Psi^\dagger (\vk) \coloneqq  \left( c_{\vk\up}^\dagger\,, c_{\kplusQ\up}^\dagger\,, c_{-\vk\down}\,, c_{\kminusQ\down} \right)
\end{equation}
and 
\begin{equation}
    h(\vk) \coloneqq  \begin{pmatrix}
        \epsilon (\vk) & \Delta_-^* & \Delta_\text{SC} & \Delta_\eta \\
        \Delta_- & \epsilon (\vk + \vQ) & \Delta_\eta & \Delta_\text{SC} \\
        \Delta_\text{SC}^* & \Delta_\eta^* & - \epsilon (-\vk) & - \Delta_+ \\
        \Delta_\eta^* & \Delta_\text{SC}^* & - \Delta_+^* & - \epsilon (-\vk - \vQ)
        \end{pmatrix}\,,
\end{equation}
where we defined $\Delta_\pm \coloneqq  \Delta_\text{CDW} \pm \Delta_\text{AFM}$.

@@

We solve the mean-field equations self-consistently.
The $\gamma$-integrals are approximated numerically using a $\tanh$-$\sinh$ quadrature \cite{takahasi73}, 
terminating once $|1 - \int \dgamma \rho(\gamma)| < 10^{-13}$ and reusing the computed points and weights.
This method excels at dealing with the singularities in the DOS, 
requiring merely a few hundred function evaluations to achieve the desired accuracy.

This procedure yields the ground state phase diagram at temperature $T=0$ shown in \autoref{fig:phase_diagram}.
The CDW-AFM boundary is located at $U = zV$, where $z$ is the coordination.
This holds for both the square lattice ($z=4$) and the simple cubic lattice ($z=6$) and can be seen by comparing \eqref{eqn:delta_cdw} and \eqref{eqn:delta_afm}:
Crossing the aforementioned line, changes which one of the two prefactors is larger.

@@

So far we have discussed the static mean-field equations that essentially describe the static ground state.
These results will be used to compute the quantities, namely expectation values, necessary for the iterated equations of motion approach \cite{uhrig09,hamerla13,hamerla14,bleicker18}.
With it, we can describe two-particle quantities like the various collective excitations of the system.
We will present the general ideas briefly here and refer the interested reader to the appendix \textcolor{red}{!REF!} for a detailed explanation and derivation.

@@

However, most Hamiltonians do not allow any such operator set to exist as the commutation usually introduces terms of higher order.
For instance, commuting a bilinear term with a quartic Hamiltonian yields, quartic terms. Repeating the commutation yields hexartic ones and so on.
Therefore, one repeats this commutation process and includes the occurring terms within a bigger set,
hoping to get better results as the set size increases.

@@

To study the collective excitation, we investigate various retarded Green's functions 
\begin{equation}
    G_{AB}^\text{ret} (t) = - i \langle [A(t), B] \rangle \Theta(t)\,,
\end{equation}
where $\Theta(t)$ is the Heaviside function, and their Fourier-transformed
\begin{equation}
    \label{eqn:standard_gf}
    G_{AB}(\omega + i0^+) = -i \int_0^{\infty} e^{izt} \langle [A(t), B] \rangle \mathrm{d}t\,.
\end{equation}
Our previous choice of pseudo scalar product enables us to write down a matrix-valued Green's functions in terms of the aforementioned matrices
\begin{align}
    \label{eqn:green_function}
    \mathcal{G}(z &= \omega + i0^+) = \mN \frac{1}{-z \mN - \mM} \mN \\
        &\coloneqq  -\mN \mathcal{R}(z) \mN\,,
\end{align}
where we used the resolvent
\begin{equation}
    \label{eqn:resolvent}
    \mathcal{R}(z) \coloneqq  \frac{1}{z \mN + \mM}\,.
\end{equation}
The entries of this matrix $\mathcal{G}(z)$ are the Fourier transformed Green's functions mentioned in \eqref{eqn:standard_gf} with respect to the operators from the initially chosen set.
For instance, assume the operator in the set is $f_{\vk}$, then the top left element of $\mathcal{G}$ is the Green's function 
\begin{equation}
    \mathcal{G}_{00}(z = \omega +i0^+) =  G(z) = -i \int_0^{\infty} \langle [f_{\vk}(t), f_{\vk}^\dagger(0)] \rangle e^{izt} \mathrm{d}t\,.
\end{equation}
For a detailed derivation of this statement, we refer the reader to the appendix \textcolor{red}{!REF!}.

Our operator set consists of operators of the type
\begin{equation}
    A_\gamma \coloneqq  \frac{1}{\sqrt{N}} \sum_{\vk} \delta (\gamma - \hat{\gamma}( \vk )) A_{\vk}\,,
\end{equation}
where $A_{\vk}$ represents each type of operator in \eqref{eqn:operators} and their Hermitian conjugates.
Different indices are taken as additional set operators, e.g. $n_{\vk \up}$, and $n_{\vk \down}$ are taken into the set separately.
We then order these operators in a way reminiscent of the $x$- and $p$-terms in the harmonic oscillator, i.e.
\begin{equation}
    X_i \coloneqq  A_i + A_i^\dagger\,,\quad P_i \coloneqq  A_i - A_i^\dagger\,.
\end{equation}
Our set is then $\mathcal{B}_{XP} \coloneqq  \{ X_i, P_i \}$.
If some operators would be 0 ($P_i$ for any $n$-type term) or duplicates (certain $X_i$ for $g$-type terms), we omit them.

@@

There are a variety of different features. The difference between the two lattices is mostly quantitative.
First and foremost, in the SC phase, there is a sharp peak located at $\omega=0$, only in the phase spectral function,
and another peak, only in the amplitude spectral function, located at $\omega=2\Delta_\text{SC}$.
We identify them with the well-known Leggett and Higgs modes in superconductors.
In the CDW phase, both of these spectral functions become identical and form a sharp peak below the two-particle continuum.

@@

\begin{figure*}
    \centering
    \includegraphics[width=.98\textwidth]{plots/sc_peak_in_cdw_position.pdf}
    \caption{The upper panels show double logarithmic plots of the positions $\omega_0$ of the SC peak in the CDW phases while the lower panels show their respective weights $w_0 = e^{b}$.
    The left column shows the results for the square and the right column for the simple cubic lattice at $U=-2.5$.
    The fits are linear, i.e., $y(V) = c \ln(V/t) + d$, and the parameters are printed on the individual panels.}
    \label{fig:sc_in_cdw_behaviour}
\end{figure*}
